% !TEX program = xelatex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\setmainfont{SFNS Display}

\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{ltablex}

\onehalfspacing
\usepackage[
  colorlinks=true,
  linkcolor=blue,
  filecolor=blue,
  urlcolor=blue,
]{hyperref}

\usepackage{color}
\definecolor{pblue}{rgb}{0.13,0.13,1}
\definecolor{pgreen}{rgb}{0,0.5,0}
\definecolor{pred}{rgb}{0.9,0,0}
\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
\definecolor{bg}{rgb}{0.96, 0.96, 0.96}

\usepackage{listings}
\lstset{language=Java,
  showspaces=false,
  showtabs=false,
  breaklines=true,
  showstringspaces=false,
  breakatwhitespace=true,
  stepnumber=1,
  numbers=left,
  commentstyle=\color{pgreen},
  keywordstyle=\color{pblue},
  stringstyle=\color{pred},
  basicstyle=\ttfamily,
  moredelim=[il][\textcolor{pgrey}]{\$\$},
  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%},
  backgroundcolor = \color{bg}
}

\renewcommand{\b}[1]{\textbf{#1}}
\renewcommand{\i}[1]{\textit{#1}}
\newcommand{\code}[1]{\texttt{#1}}

\newcommand{\gh}[1]{%
  \href{https://github.com/awave1/ObjectInspector/commit/#1}{#1}%
}

\title{\b{CPSC 501 -- Assignment 2}}

\author{\b{Artem Golovin} \\ 30018900}
\date{}

\begin{document}
\maketitle

\section*{Overview}

\href{https://github.com/awave1/ObjectInspector}{\code{ObjectInspector}} is a reflective object inspector. It performs complete object inspection at a runtime. \code{Inspector} handles the object inspection. General project setup is described in project \href{https://github.com/awave1/ObjectInspector#reflective-object-inspector}{README.md}. Project can also be found on GitLab \href{https://gitlab.cpsc.ucalgary.ca/artem.golovin/ObjectInspector}{artem.golovin/ObjectInspector}

\section*{Refactoring}

Some refactoring was done to the project after the working version was implemented. The following is the list of commits with description of what refactoring was done

\subsection*{Implement \code{InspectorResult} to store inspected information; Implement \\ \code{FieldPair} to make it easier to test object inspection \gh{e9870e19}, \gh{d6a2812c}}

It was necessary to implement some sort of storage for object inspection in order to test the \\ \code{Inspector\#inspect(Object, boolean)} properly. \href{https://github.com/awave1/ObjectInspector/blob/master/src/main/java/inspector/InspectorResult.java}{\code{InspectorResult}} contains different \code{HashMap}s to store inspected information about object. Using that class, we can test the \code{inspect} method without having to compare outputs.

\subsection*{Use \code{IndentedOutput} interface and use custom \code{forEach} to iterate array (\gh{645bfdce})}

Since the output needs to be indented in order to make it easier to read and to say which values are nested, \href{https://github.com/awave1/ObjectInspector/blob/master/src/main/java/utils/IndentedOutput.java}{\code{IndentedOutput}} and method \href{https://github.com/awave1/ObjectInspector/blob/master/src/main/java/inspector/Inspector.java#L199}{\code{indentOutput}} helps to achive that result. Originally, indentation was calculated per each \code{inspect} method. To remove duplicated code, \href{https://github.com/awave1/ObjectInspector/blob/master/src/main/java/inspector/Inspector.java#L199}{\code{indentOutput}} method was added.

\subsection*{Extract value inspection into its own method (\gh{c039ea3e})}

\code{inspectArray} and \code{inspectField} were performing the same tasks, therefore to eliminate redundant code, \href{https://github.com/awave1/ObjectInspector/blob/master/src/main/java/inspector/Inspector.java#L181}{\code{inspectValues}} method was added.

\section*{Git Log}
\input{log.tex}

\end{document}
